---
title: "Logistic Regression Excercise"
author: "Afif"
date: "February 3, 2019"
output: github_document
---

***

##Problem Statement

Use the NH11 data set that we loaded earlier.

1. Use glm to conduct a logistic regression to predict ever worked
   (everwrk) using age (age_p) and marital status (r_maritl).
2. Predict the probability of working for each level of marital
   status.

   Note that the data is not perfectly clean and ready to be modeled. You
   will need to clean up at least some of the variables before fitting
   the model.

***

##Solution

First is to load the data, and check the summary the three necessary variables : ever worked (everwrk), age (age_p), and marital status (r_maritl).
```{r}
NH11 <- readRDS("NatHealth2011.rds")
NH11.small <- data.frame(everwrk=NH11$everwrk, age_p=NH11$age_p,r_maritl=NH11$r_maritl)
summary(NH11.small)
```

From the summary result above, the dependent variables everwrk has quite a lot of missing datas, and quite a few of unnecessary levels : Refused, Uncertain, and Don't Know. Next step will be to filter out all missing and unnecessary data. 
```{r}
#Filter out all levels other than the necessary ones = "1 Yes" and "2 No"
NH11.small$everwrk <- factor(NH11.small$everwrk, levels=c("1 Yes","2 No")) 
#Drop unused levels
NH11.small$r_maritl <- droplevels(NH11.small$r_maritl)
#Remove observations with missing data
NH11.small<- NH11.small[!is.na(NH11.small$everwrk), ]
summary(NH11.small)
```

Then, to create the logistic regression model using glm model, and examining its summary.

```{r}
everwrk.log <- glm(everwrk ~ age_p + r_maritl, data=NH11.small, family="binomial")
summary(everwrk.log)

```
Lastly, is to actually predict the effect of marital status with chance of a person ever working. For this purpose we will examine the result of Effect () function using plot.

```{r fig.height =6 , fig.width = 6}
library(effects)
r_maritl.effect <- Effect("r_maritl", everwrk.log)
plot(r_maritl.effect,axes=list(grid=FALSE, x=list(cex=0.6,rug = FALSE, rotate=45)))
```